### 2013-02-13 doc/xps2013/proposal.tex
updated collab section & bib 	modified:   doc/xps2013/proposal.bib 	modified:   doc/xps2013/proposal.tex

We expect this hierarchical organization will reduce scaling requirements from
\BigO{n^2} threads to \BigO{n \times log(n)}. Of course, it takes what used to
be a single network hop for communication and turns it into \BigO{log(n)}
hops. More threads will be required to overcome this increased latency, but we
hypothesize only \BigO{log(n)} more, hence a real \BigO{n / log(n)^2} scaling
benefit is achievable with the a virtual hierarchical network topology.

@@

Kahan has tremendous experience in ... from Tera/Cray ... {\bf SIMON PUT YOUR STUFF HERE.}

>>>>

We expect this hierarchical organization will reduce scaling requirements from
\BigO{n^2} threads to \BigO{n \times log(n)}. Of course, it takes what used to
be a single network hop for communication and turns it into \BigO{log(n)}
hops. More threads will be required to overcome this increased latency, but we
hypothesize only \BigO{log(n)} more, hence a real \BigO{n / log(n)^2} scaling
benefit is achievable with a virtual hierarchical network topology.

@@

Kahan has been working in the area of parallel computing for irregular
applications for twenty years, largely in industry.  At Cray (previously Tera
Computer) he developed the runtime system~\cite{Alverson95schedulingon,Alverson97terahardware-software} and combining memory allocator~\cite{MAMA} still in production use on
Cray's XMT system in which over 50,000 threads execute concurrently sharing one
global address space.  He has co-authored patents and publications for both of these
systems as well as for a scalable connected components graph algorithm that bears
his name~\cite{Underwood07analyzingthe}.
Kahan originated and for three years has been co-PI for the Grappa project.
